A framework for adaptive width control of dense contour-parallel toolpaths in \revise{additive manufacturing}{fused deposition modeling}\censornotice

### 2020-01-22 0_main.tex
censoring options

@@

	\newcommand{\censoromit}[1]{}
	%\newcommand{\censoromit}[1]{#1}
    % \StopCensoring

@@

	% Revise macro (usage: \revise{old}{new})
	% Version a) First arg red and striked out, second argument green
	%\newcommand{\revise}[2]{\textcolor{red}{\stkout{#1}}\textcolor{blue}{#2}}
	%\newcommand{\revise}[2]{{\color{red}{#1}\color{blue}{#2}}}
	% Version b) First arg ignored, second argument green
	\newcommand{\revise}[2]{{\color{blue}{#2}}}
	% Version c) First arg ignored, second argument unchanged (for final draft)
	%\newcommand{\revise}[2]{#2}
	%\newcommand{\revise}[2]{#1}

@@

\title{A framework for adaptive width control of dense contour-parallel toolpaths in \revise{additive manufacturing}{fused deposition modeling}}

>>>>

	\newif\ifcensor
	\newif\ifcolorrevise

	\censortrue
	\colorrevisefalse

@@

    \newcommand{\censoromit}[1]{}
	\newcommand{\censornotice}{}
	\ifcensor
		\renewcommand{\censornotice}{\\Anonymized 2020 (under revision)}
	\else
		\renewcommand{\censoromit}[1]{#1}
		\StopCensoring
    \fi

@@

	% Revise macro (usage: \revise{old}{new})
	\newcommand{\revise}[2]{#2}
	% Version a) First arg red and striked out, second argument green
	%\newcommand{\revise}[2]{\textcolor{red}{\stkout{#1}}\textcolor{blue}{#2}}
	%\newcommand{\revise}[2]{{\color{red}{#1}\color{blue}{#2}}}
	% Version b) First arg ignored, second argument green
	\ifcolorrevise
	\renewcommand{\revise}[2]{{\color{blue}{#2}}}
	\fi
	% Version c) First arg ignored, second argument unchanged (for final draft)
	%\newcommand{\revise}[2]{#2}
	%\newcommand{\revise}[2]{#1}

@@

\title{A framework for adaptive width control of dense contour-parallel toolpaths in \revise{additive manufacturing}{fused deposition modeling}\censornotice}
